\documentclass[11pt,a4paper]{article}

\usepackage[a4paper,margin=2.5cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{parskip}

\definecolor{ph}{HTML}{B00020}
\newcommand{\ph}[1]{{\color{ph}\textbf{[#1]}}}

\titleformat{\section}{\large\bfseries}{\thesection.}{0.6em}{}
\titlespacing*{\section}{0pt}{1.4em}{0.4em}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\fancyhead[L]{\small Jess Trading}
\fancyhead[R]{\small Privacy Policy}
\fancyfoot[C]{\small Page \thepage}

\setlist[itemize]{leftmargin=1.4em,topsep=0.2em,itemsep=0.2em}

\begin{document}

\thispagestyle{fancy}

{\Huge\bfseries Privacy Policy}\\[0.4em]
{\large Jess Trading (JessTradingBots)}\\[0.3em]
{\small Last updated: 8 June 2026}

\vspace{0.6em}
\hrule
\vspace{1em}

This Privacy Policy explains how we collect, use and protect your personal data when you visit our
website, join our list, or purchase the Range Breakout Bot. We process personal data in accordance
with the EU General Data Protection Regulation (GDPR) and Spanish data-protection law (LOPDGDD).

\section{Data controller}
The data controller is Joaquin Esperon Solari, an individual resident in Spain, NIF 42378795F,
address Carrer Major 22, Costitx, Illes Balears, 07144, Spain, trading as ``Jess Trading'' /
``JessTradingBots''. Contact for any privacy matter:
\href{mailto:jesstradesinfobot@gmail.com}{jesstradesinfobot@gmail.com}.

\section{Personal data we collect}
\begin{itemize}
  \item \textbf{Data you give us:} your email address when you join our mailing list or request the
  free guide, and the details needed to complete and support a purchase.
  \item \textbf{Purchase data:} processed by Whop, our marketplace and payment processor. We receive
  confirmation of your purchase and the associated email. We do not store your full payment-card
  details --- those are handled by Whop and its processors.
  \item \textbf{Usage and device data:} standard analytics and advertising data (pages visited,
  referrer, device and browser type, approximate location) collected through cookies and tracking
  pixels.
\end{itemize}
We do not intentionally collect special categories of data, and we do not ask for your broker
credentials or access to your trading account.

\section{Purposes and legal bases}
We process personal data on the following GDPR legal bases:
\begin{itemize}
  \item \textbf{Performance of a contract} (Art.~6(1)(b)) --- to deliver the Product, provide setup
  support, and handle refunds.
  \item \textbf{Consent} (Art.~6(1)(a)) --- to send you the free guide and marketing emails, and to
  set non-essential cookies and advertising pixels. You can withdraw consent at any time.
  \item \textbf{Legitimate interests} (Art.~6(1)(f)) --- to measure and improve our marketing, to
  secure our systems, to prevent fraud, and to enforce our terms.
  \item \textbf{Legal obligation} (Art.~6(1)(c)) --- to meet accounting, tax and consumer-law
  obligations.
\end{itemize}

\section{Cookies and tracking}
We use cookies and the Meta (Facebook) Pixel, including its Conversions API, to understand how
visitors find and use the site and to measure advertising performance. You can disable cookies in
your browser settings; some features may not work as intended if you do.

\section{Who we share data with}
We share personal data only with the service providers needed to run the business, acting as our
processors or independent controllers:
\begin{itemize}
  \item \textbf{Whop} --- marketplace, checkout and payment processing.
  \item \textbf{Our email provider} --- to deliver the guide and any emails you opted into.
  \item \textbf{Meta / advertising and analytics platforms} --- to measure and run advertising.
\end{itemize}
We do not sell your personal data.

\section{International transfers}
Some providers (for example Meta and certain payment infrastructure) are based outside the European
Economic Area, including in the United States. Where personal data is transferred outside the EEA,
it is protected by appropriate safeguards such as the European Commission's Standard Contractual
Clauses or an adequacy decision.

\section{Retention}
We keep your personal data only for as long as necessary for the purposes above and to meet legal,
tax and accounting obligations, after which it is deleted or anonymised. Marketing data is kept
until you unsubscribe or withdraw consent.

\section{Security}
We apply reasonable technical and organisational measures to protect personal data against
unauthorised access, loss or misuse. No method of transmission or storage is completely secure, and
we cannot guarantee absolute security.

\section{Your rights}
Under the GDPR you have the right to: access your data; rectify inaccurate data; erase your data;
restrict or object to processing; data portability; and to withdraw consent at any time without
affecting prior lawful processing. To exercise any right, email
\href{mailto:jesstradesinfobot@gmail.com}{jesstradesinfobot@gmail.com}. You can unsubscribe from
marketing emails using the link in any message.

You also have the right to lodge a complaint with the Spanish Data Protection Agency (Agencia
Espanola de Proteccion de Datos, AEPD --- \href{https://www.aepd.es}{www.aepd.es}) or your local
supervisory authority.

\section{Children}
The Product and website are not directed at anyone under 18, and we do not knowingly collect data
from minors.

\section{Changes to this policy}
We may update this Privacy Policy from time to time. The ``Last updated'' date above reflects the
most recent revision.

\section{Contact}
Privacy questions or requests:
\href{mailto:jesstradesinfobot@gmail.com}{jesstradesinfobot@gmail.com} ---
\href{https://jesstrading.xyz}{jesstrading.xyz}.

\end{document}
