\documentclass[11pt,a4paper]{article}

\usepackage[a4paper,margin=2.5cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{parskip}

\definecolor{ph}{HTML}{B00020}
\newcommand{\ph}[1]{{\color{ph}\textbf{[#1]}}}

\titleformat{\section}{\large\bfseries}{\thesection.}{0.6em}{}
\titlespacing*{\section}{0pt}{1.4em}{0.4em}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\fancyhead[L]{\small Jess Trading}
\fancyhead[R]{\small Return \& Refund Policy}
\fancyfoot[C]{\small Page \thepage}

\setlist[itemize]{leftmargin=1.4em,topsep=0.2em,itemsep=0.2em}

\begin{document}

\thispagestyle{fancy}

{\Huge\bfseries Return \& Refund Policy}\\[0.4em]
{\large Jess Trading (JessTradingBots)}\\[0.3em]
{\small Last updated: 8 June 2026}

\vspace{0.6em}
\hrule
\vspace{1em}

We would rather lose a sale than create an unhappy customer. Every purchase of the Range Breakout
Bot comes with a \textbf{14-day, no-questions-asked refund window}.

\section{The 14-day window}
You have 14 days from the date of purchase to request a full refund for any reason. Try the Bot on a
small or demo account, judge it for yourself, and if it is not for you, get your money back.

\section{Your EU right of withdrawal}
As a consumer in the EU you have a statutory right to withdraw from a distance contract within 14
days. The Product is digital content delivered electronically. Where you ask for immediate access
and acknowledge that you lose the statutory withdrawal right once download begins, that statutory
right may no longer apply --- but our voluntary 14-day refund described above still does, and it is
at least as favourable to you. Nothing in this policy removes any mandatory consumer right you have
under applicable law.

\section{How to request a refund}
Refunds are handled through Whop, our marketplace and payment processor. You can:
\begin{itemize}
  \item use the refund option inside your Whop dashboard; or
  \item email \href{mailto:jesstradesinfobot@gmail.com}{jesstradesinfobot@gmail.com} with the email
  address you used at checkout, and we will process it for you.
\end{itemize}

\section{When the refund is processed}
Approved refunds are issued to your original payment method. Processing time depends on Whop and
your bank or card issuer and typically takes a few business days.

\section{After the window}
Because the Product is a digital file delivered instantly, purchases are non-refundable after the
14-day window has passed, except where a mandatory consumer right requires otherwise.

\section{Abuse}
The refund window is offered in good faith. We reserve the right to decline a refund where we detect
abuse --- for example repeated buy-and-refund cycles, or evidence that the \texttt{.ex5} file has
been copied, shared or redistributed in breach of the EULA or Terms of Service.

\section{Contact}
Questions about a refund:
\href{mailto:jesstradesinfobot@gmail.com}{jesstradesinfobot@gmail.com} ---
\href{https://jesstrading.xyz}{jesstrading.xyz}.

\end{document}
