\documentclass[11pt,a4paper]{article}

\usepackage[a4paper,margin=2.5cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{parskip}

\definecolor{rule}{HTML}{101010}
\definecolor{ph}{HTML}{B00020}

\newcommand{\ph}[1]{{\color{ph}\textbf{[#1]}}}

\titleformat{\section}{\large\bfseries}{\thesection.}{0.6em}{}
\titlespacing*{\section}{0pt}{1.4em}{0.4em}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0.4pt}
\fancyhead[L]{\small Jess Trading}
\fancyhead[R]{\small Terms of Service}
\fancyfoot[C]{\small Page \thepage}

\setlist[itemize]{leftmargin=1.4em,topsep=0.2em,itemsep=0.2em}

\begin{document}

\thispagestyle{fancy}

{\Huge\bfseries Terms of Service}\\[0.4em]
{\large Jess Trading (JessTradingBots)}\\[0.3em]
{\small Last updated: 8 June 2026}

\vspace{0.6em}
\hrule
\vspace{1em}

\section{About these Terms}
These Terms of Service (the ``Terms'') govern the sale and use of the Range Breakout Bot and related
materials sold under the brand ``Jess Trading'' / ``JessTradingBots''. By purchasing or using the
Product you accept these Terms in full. If you do not agree, do not purchase or use the Product.

The Product is sold by Joaquin Esperon Solari, an individual resident in Spain, NIF 42378795F, with
address at Carrer Major 22, Costitx, Illes Balears, 07144, Spain (the ``Operator'', ``we'', ``us'').
You can contact us at \href{mailto:jesstradesinfobot@gmail.com}{jesstradesinfobot@gmail.com}.

\section{Definitions}
\begin{itemize}
  \item \textbf{Product / Bot} --- the Range Breakout Bot: a MetaTrader~5 (MT5) Expert Advisor
  delivered as an \texttt{.ex5} file, together with the setup guide, video walkthrough and
  pre-configured settings supplied with it.
  \item \textbf{Platform} --- Whop, the third-party marketplace and payment processor through which
  the Product is sold and delivered (operated by Whop Inc.).
  \item \textbf{You / Customer} --- the person who purchases or uses the Product.
\end{itemize}

\section{The Product}
The Product is software that runs a rule-based range breakout strategy on XAUUSD and four major
forex pairs (EURUSD, GBPUSD, USDJPY, EURJPY) inside the MetaTrader~5 terminal, according to
parameters you configure. The Product is a tool only. It does not open an account for you, does not
hold your funds, and does not manage your money. Your capital remains with your own broker at all
times.

\section{Eligibility}
You must be at least 18 years old and legally able to enter into a contract in your jurisdiction.
You are responsible for ensuring that the use of automated trading software and the trading of
forex / CFD instruments is lawful where you live.

\section{Purchase, price and payment}
All purchases are processed by the Platform (Whop). The price shown at checkout is a one-time
payment for a lifetime licence, unless stated otherwise at the point of sale. Taxes may be added
depending on your location. We do not store your full card details --- payment data is handled by
the Platform and its processors.

\section{Licence}
Your right to use the Product is granted under the End User Licence Agreement (EULA) supplied with
the Product. In summary, you receive a non-exclusive, non-transferable, lifetime licence to use the
Bot on the number of MT5 accounts stated at checkout (up to two). You may not resell, redistribute,
share or reverse-engineer the Product. The full terms are in the EULA, which forms part of these
Terms.

\section{Refunds}
Refunds are governed by our Return Policy, which offers a 14-day, no-questions-asked refund window.
Nothing in these Terms removes any mandatory refund or withdrawal rights you have as a consumer
under EU law.

\section{No financial advice}
We are not a broker, investment firm, financial adviser, or registered investment professional. The
Product, our website, our communications and any figures we publish do not constitute investment,
financial, tax or legal advice, nor a solicitation or recommendation to trade any instrument. You
are solely responsible for your own trading decisions, your choice of broker, your capital
allocation and your risk settings.

\section{No guarantee of results; trading risk}
Trading forex and CFDs, including XAUUSD, carries a high level of risk and may not be suitable for
all investors. Leverage can work against you as well as for you, and depending on your broker and
leverage your losses may exceed your initial deposit. Past performance --- including backtests, demo
accounts and live tracker data --- is not indicative of future results. We make no representation or
warranty that the Product will be profitable or will avoid losses. You use the Product entirely at
your own risk. The full risk warning is set out in our Risk Disclosure.

\section{Acceptable use and restrictions}
You agree not to: (a) copy, resell, sublicense, rent, lend, distribute or publish the Product or its
settings; (b) decompile, disassemble or reverse-engineer the Product, or attempt to extract its
underlying logic; (c) use the Product for any unlawful purpose; or (d) misrepresent the Product, its
performance, or your relationship with us. Breach of this section terminates your licence without
refund.

\section{Intellectual property}
The Product, including the \texttt{.ex5} file, the strategy logic, the brand, text, graphics and
materials, is owned by the Operator and protected by intellectual property law. No ownership is
transferred to you --- you receive a licence to use, not title to the software.

\section{Disclaimer of warranties}
To the maximum extent permitted by law, the Product is provided ``as is'' and ``as available'',
without warranties of any kind, whether express or implied, including any implied warranties of
merchantability, fitness for a particular purpose, profitability, or non-infringement. We do not
warrant that the Product will be uninterrupted, error-free, compatible with every broker or MT5
build, or that it will meet your expectations.

\section{Limitation of liability}
To the maximum extent permitted by law, the Operator shall not be liable for any trading losses,
lost profits, lost opportunities, or any indirect, incidental, special, consequential or punitive
damages arising out of or relating to the Product or these Terms, even if advised of the possibility
of such damages. Our total aggregate liability for any claim arising out of or relating to the
Product is limited to the amount you actually paid for the Product. Nothing in these Terms limits
liability that cannot be limited under applicable law (including liability for fraud or for death or
personal injury caused by negligence), nor your mandatory rights as a consumer.

\section{Indemnity}
You agree to indemnify and hold harmless the Operator from any claim, loss or expense arising out of
your breach of these Terms or your unlawful or improper use of the Product.

\section{Suspension and termination}
We may suspend or terminate your licence if you breach these Terms or the EULA. On termination you
must stop using the Product and delete all copies. Sections that by their nature should survive
(intellectual property, disclaimers, limitation of liability, governing law) survive termination.

\section{Third-party platform}
Sales, delivery and payments occur through Whop, which has its own terms and privacy policy. We are
not responsible for the Platform's availability or conduct. Disputes about payment processing may
also be subject to the Platform's rules.

\section{Changes}
We may update the Product and these Terms from time to time. The ``Last updated'' date reflects the
most recent revision. Material changes will apply to purchases and use after they take effect.

\section{Governing law and jurisdiction}
These Terms are governed by the laws of Spain. Subject to any mandatory consumer-protection rules
that grant you the right to bring proceedings in your country of residence, the courts of
Illes Balears, Spain shall have jurisdiction over any dispute.

\section{Contact}
Questions about these Terms: \href{mailto:jesstradesinfobot@gmail.com}{jesstradesinfobot@gmail.com}
--- \href{https://jesstrading.xyz}{jesstrading.xyz} --- Instagram
\href{https://www.instagram.com/jesstradingbots/}{@jesstradingbots}.

\end{document}
